User-level Grid Monitoring with Inca 2

### 2007-04-17 pubs/papers/hpdc-gmw-2007/paper.tex
fix font in code listings
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6857 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

\lstset{
  basicstyle=\scriptsize\ttfamily, 
  frame=single,
  keywordstyle=\textbf, 
  identifierstyle=, 
  commentstyle=\scriptsize\ttfamily, 
  stringstyle=\ttfamily, 
  numbers=left, 
  numberstyle=\scriptsize,
  stepnumber=2,
  firstnumber=1,
  showstringspaces=false} 
\begin{figure}[tbp]
\lstset{language=Perl} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing}}
\lstset{language=XML,keywordstyle={}} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing.out}}
\caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
availability of a Globus GRAM server and (b) sample of its output.}
\end{figure}

>>>>

\lstset{
  basicstyle=\scriptsize\fontfamily{phv}\selectfont, 
  frame=single,
  keywordstyle=\textbf, 
  identifierstyle=, 
  commentstyle=\scriptsize, 
  stringstyle=, 
  numbers=left, 
  numberstyle=\scriptsize,
  stepnumber=2,
  firstnumber=1,
  showstringspaces=false} 
\begin{figure}[tbp]
\lstset{language=Perl} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing}}
\lstset{language=XML,keywordstyle={}} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing.out}}
\caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
availability of a Globus GRAM server and (b) sample of its output.}
\end{figure}
